Untrusted B2B Collaboration using the Blockchain

### 2018-07-04 paper/paper.tex
add figures to paper

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jonas Beyer \and
Philipp Otto\and
S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Hasso-Plattner-Institut für Digital Engineering gGmbH, Prof.-Dr.-Helmert-Str. 2-3, Potsdam 14482, Germany\\
\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

@@

>>>>

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jonas Beyer \and
Philipp Otto\and
S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Hasso-Plattner-Institut für Digital Engineering gGmbH, Prof.-Dr.-Helmert-Str. 2-3, Potsdam 14482, Germany\\
\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Blockchain technology enables untrusting parties to have trusted communication. We use this to implement a conversion of BPM choreographies to smart contracts on the Ethereum Blockchain.

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig/system_diagram.eps}
\caption{The architecture of our design.} \label{fig1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{fig/initialization.eps}
\caption{An initialization process.} \label{fig2}
\end{figure}
